### 2014-03-24 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update report

\section{Heat Release Rate}
\label{HRR}
The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation. Here, we examine the data to examine the impact of ventilation on fire size. Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios. The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).

@@

In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions). The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur. The dash-dotted line is the prescribed FDS input HRR. We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR. The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited. The HRR drops to 5 MW as the available oxygen inside the structure gets consumed. There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents. Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s. After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW. The HRR then begins to increase towards a sustainable steady state value.

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door. Therefore, the following analysis will focus on the results of the baseline simulation results.

@@

\section{Temperature}
For analysis of the predicted simulation temperatures, the analysis will focus on the high hazard areas of the structure: the attic, the rear porch and connecting stairwell, and the interior hallway which connects the rear porch to the front stairwell. Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions. The first time to consider is just before a firefighter opened the rear porch door (cf. Fig.~(\ref{fig:temp_129s})).

@@

>>>>

\section{Heat Release Rate}
\label{HRR}
The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation. Here, we examine impact of ventilation on fire size. Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios. The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).

@@

In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions). The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur. The dash-dotted line is the prescribed FDS input HRR. We can see that within the first 10 seconds, the structure is under-ventilated as the modeled HRR is below the prescribed HRR. The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited. The HRR drops to 5 MW as the available oxygen inside the structure gets consumed. There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents. Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s. After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW. The HRR then begins to increase towards a sustainable steady state value.

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters inside the structure. Therefore, the continued analysis will focus on the results of the baseline simulation results.

@@

\section{Temperature}
Analysis of the predicted simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell. Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions. The first times are 129 seconds into the simulation, just before a firefighter opened the rear porch door (cf. Fig.~(\ref{fig:temp_129s})) and 159 seconds into the simulation, just before the interior door fails (cf. Fig.~(\ref{fig:temp_159s})).

@@

The
